A weakly structured stem for human origins in Africa

### 2023-01-08 paper.tex
Acknowledgements / accessions #

All sequencing data are available from XXX,
accession number: YYY.

@@

We are grateful for the DNA contribution from each participant which enabled
this study; in particular we wish to highlight the generous participation of
the Richtersveld Nama community in South Africa and help from local research
assistants Willem DeKlerk and Hendrik Kaimann. Additional assistance and
community engagement was conducted by Justin Myrick, Chris Gignoux, Caitlen
Uren and Cedric Werely. We thank the African Genome Diversity Project for data
generation, including Tommy Carensten, Deepti Gurdasani, and Manj Sandhu. We
thank Luke Anderson-Trocm\'e and Georgette Femerling for assistance in creating
the map in Figure~\ref{fig:diversity} and Figure \ref{fig:toymodels},
respectively. This research was supported by an NIH grant R35GM133531 (to BMH).
The content is solely the responsibility of the authors and does not
necessarily represent the official views of the National Institutes of Health.

>>>>

Nama sequencing data are available from the European Genome-Phenome Archive (EGA),
accession number: EGAD00001006198. The African Diversity Reference Panel can be
found at accession: EGAS00001000960.

@@

We are grateful for the DNA contribution from each participant which enabled
this study; in particular we wish to highlight the generous participation of
the Richtersveld Nama community in South Africa and help from local research
assistants Willem DeKlerk and Hendrik Kaimann. Additional assistance and
community engagement was conducted by Justin Myrick, Chris Gignoux, Caitlen
Uren and Cedric Werely. We thank the African Genome Diversity Project for data
generation, including Tommy Carensten, Deepti Gurdasani, and Manj Sandhu. We
thank Luke Anderson-Trocm\'e and Georgette Femerling for assistance in creating
the map in Figure~\ref{fig:diversity} and Figure \ref{fig:toymodels},
respectively. We thank Nuria Melisa Morales-Garcia for designing Figure \ref{fig:proposed-models} 
and \ref{fig:best-fit-models}, and extensive data visualization discussion. 
This research was supported by an NIH grant R35GM133531 (to BMH).
The content is solely the responsibility of the authors and does not
necessarily represent the official views of the National Institutes of Health.
